Pesticides pollution of small streams in Germany

### 2016-08-10 article.tex
started pollution section

The four groups were:
i) small, agricultural streams (catchment size \textless 30 km\textsuperscript{2} and \textgreater 40\% agriculture);
ii) small, non-agricultural streams (catchment size \textless 30 km\textsuperscript{2} and \textless 10\% agriculture);
iii) medium sized, agricultural streams (30 km\textsuperscript{2} $\ge$catchment size \textless 150 km\textsuperscript{2} and \textgreater 40\% agriculture)
iv) medium sized, non-agricultural streams (30 km\textsuperscript{2} $\ge$catchment size \textless 150 km\textsuperscript{2} and \textless 10\% agriculture)

>>>>

The four groups were:
i) small, agricultural streams (catchment size \textless 30 km\textsuperscript{2} and agriculture \textgreater 40\%, n = 842 sites);
ii) small, non-agricultural streams (catchment size \textless 30 km\textsuperscript{2} and agriculture \textless 10\%, n = 254 sites);
iii) medium sized, agricultural streams (30 km\textsuperscript{2} $\le$ catchment size \textless 150 km\textsuperscript{2} and agriculture \textgreater 40\%, n = 489 sites);
iv) medium sized, non-agricultural streams (30 km\textsuperscript{2} $\le$ catchment size \textless 150 km\textsuperscript{2} and agriculture \textless 10\%, n = 160 sites).
